---
title: "Harvesting the Web - Benjamin Kampka - 35017"
output: html_notebook
---

# Harvesting the web with rvest

```{r}
library(tidyverse)
library(rvest)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

```{r}
lego_url <- "http://www.imdb.com/title/tt1490017/"
html <- read_html(lego_url)
characters <- html_nodes(html, ".cast_list .character")
length(characters)
```

```{r}
characters[1:2]
```

```{r}
html_text(characters, trim=TRUE)
```

rvest contains a few handy functions for accessing different attributes of the currently selected nodes. For example, we can access names of the selected tags with html_name():

```{r}
html_nodes(html,".cast_list") %>% 
  html_name()
```

```{r}
html_node(html,".cast_list")
```

```{r}
html_node(html,".cast_list") %>% 
  html_table() %>% 
  head()
```
```{r}
html_node(html, ".cast_list .character") %>% 
  html_text()
```

```{r}
html_nodes(html, ".cast_list .character") %>% 
  html_children() %>% 
  html_attr("href")
```

```{r}
html_node(html, ".cast_list .character") %>% 
  html_children() %>% 
  html_text()
```

```{r}
html_node(html, ".cast_list .character") %>% 
  html_nodes(xpath="./text()[normalize-space()]")
```

```{r}
html_node(html, ".cast_list .character") %>% 
  html_nodes(xpath="./text()[normalize-space()]") %>% 
  html_text(trim=TRUE)
```

# SelectorGadget tutorial

```{r}
cast <- html_nodes(html, ".primary_photo+ td a")
length(cast)
```

```{r}
cast[1:2]
```

Extract text from the HTML nodes:

```{r}
html_text(cast, trim = TRUE)
```

We can access html attributes of the selected nodes using html_attrs().

```{r}
cast_attrs <- html_attrs(cast)
length(cast_attrs)
cast_attrs[1:2]

```

As we can see there’s only one attribute called href which contains relative url to the actor’s page. We can extract it using html_attr(), indicating the name of the attribute of interest. Relative urls can be turned to absolute urls using url_absolute().

```{r}
cast_abs_urls <- html_attr(cast, "href") %>% url_absolute(lego_url)
cast_abs_urls
```

# rvest Documentary

## Test mit "Die Veruteilten"

Rating:

```{r}
die_verurteilten<- read_html("https://www.imdb.com/title/tt0111161/")
rating <- die_verurteilten %>% html_nodes("strong span") %>% html_text() %>% as.numeric()
rating
```

Cast:
```{r}
cast <- die_verurteilten %>%
  html_nodes("#titleCast .primary_photo img") %>%
  html_attr("alt")
cast
```

Poster:

```{r}
poster <- die_verurteilten %>%
  html_nodes(".poster img") %>%
  html_attr("src")
poster
```